The coverage fraction of starspots on young Taurus members and consequences for stellar ages estimates at 1$-$10 Myr

### 2018-03-27 document/ms.tex
Worked on the paper at the Palo Alto library which is a nice library.

\shorttitle{Physical properties of spotted Taurus members}

@@

Wow, starspots are everywhere, look at this paper from Brett Morris \citep{}.

@@

\subsection{IGRINS Spectroscopy}\label{sec:igrins}
Here are some citations:

>>>>

\shorttitle{Extreme Starspots in Taurus}

@@

The evolutionary state of a star can be superbly predicted with an age and a mass.  Angular momentum and metallicity further improve those predictions.  Unfortunately the age of a star cannot be trivially measured.  Pre-main sequence isochronal methods provide only coarse estimates of cluster ages, with perhaps 100\% uncertainties attributable to both intrinsic scatter and systematic bias.  Isochronal models generally ignore angular momentum, a safe bet after stars have resided on the pre-main-sequence for much longer than their formation timescale.  Pre-main sequence stars differ.  For the first $1-100$ Myr of a star's life, the rotation rate of a star may inhibit convective efficiency, making the star dwell in its puffed-up, larger-than-expected radius, in order to allow the same amount of internal energy to escape.  The extra-high rotation rates of young stars interplay with both global and surface magnetic fields and environmental factors to yield complex evolutionary phenomena.

One observational manifestation of rotationally-heightened magnetic fields is the presence of \emph{starspots}.  Starspots serve as a familiar---albeit inexact---avenue through which we can quantify possible limitations to isochronal age estimates.  Importantly, starspots possess many favorable observational properties that form the central thrust of this paper.  In our previous paper \citep{2017ApJ...836..200G}, we combined multiple datasets to reveal a large $\sim75\%$ coverage fraction of starspots on the surface of the Weak-Lined T-Tauri Star (WTTS) LkCa~4.  Here we seek to identify whether LkCa~4 merely represents an extreme outlier, or whether other WTTS's can possess similiarly large starspots.

We first emphasize possible geometric degeneracies that can give rise to larger-than-expected starspots.  We then collate numerous photometric and spectroscopic data sources (Section XXX), and their starspot-centric analyses (Section XXX).  We combine inferences on our small sample of stars to assess the effect of starspots on the pre-main sequence HR-diagram (Section XXX).  Finally we question our initial assumptions in Section XXX.

@@

\subsection{IGRINS Spectroscopy}\label{sec:igrins}

Recently, \citet{2017ApJ...836..200G} found evidence for a large starspots on the Weak-Lined T-Tauri Star LkCa 4.
Here are some citations:
